Results

### 2019-05-02 analysis/survey/preregistration.Rmd
Added comments to the pre-registration

@@

@@

@@

TODO: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity.

@@

TODO: NA?

>>>>

COMMENT: I don't see a need to index (i.e., use dimension reduction). We should just be collapsing covariates via Transformations in a way motivated by your experience and theory with respect to the "competing sets of covariates in the distribution of heterogeneity" that we'd like to use to compare effects on the marginal posteriors of the preference parameters.

@@

COMMENT: See comment for Indices.

@@

COMMENT: No, it's really just looking at/comparing the posterior marginals on their own vs. the posterior marginals with different covariates includes, plus the market simulation.

@@

COMMENT: Specify what the "competing sets of covariates" are that we'll include in the distribution of heterogeneity. This should be the motivation of the collapses specified in Transformations.

@@

NA.
